Comparing \pkg{binsegRcpp} with other implementations of binary segmentation for change-point detection

### 2025-05-07 figure-heap-refs-other.tex
N^1.4

% Created by tikzDevice version 0.12.6 on 2025-05-06 22:53:33
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,172.40) --
	( 69.87,134.54) --
	( 84.71,140.87) --
	( 99.55,145.53) --
	(114.40,152.07) --
	(129.24,157.56) --
	(144.08,162.96) --
	(158.92,168.49) --
	(173.77,174.13) --
	(188.61,179.84) --
	(203.45,185.59) --
	(218.29,191.36);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 44.40) --
	(226.46, 44.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 71.59) --
	(226.46, 71.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 98.78) --
	(226.46, 98.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 58.00) --
	(226.46, 58.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 85.19) --
	(226.46, 85.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,112.38) --
	(226.46,112.38);

@@

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 58.00) --
	( 69.87, 61.60) --
	( 84.71, 59.31) --
	( 99.55, 59.71) --
	(114.40, 58.63) --
	(129.24, 59.16) --
	(144.08, 61.71) --
	(158.92, 72.45) --
	(173.77, 81.74) --
	(188.61, 90.10) --
	(203.45, 98.38) --
	(218.29,109.54) --
	(218.29,109.46) --
	(203.45, 98.22) --
	(188.61, 86.26) --
	(173.77, 76.01) --
	(158.92, 66.75) --
	(144.08, 59.17) --
	(129.24, 54.26) --
	(114.40, 53.86) --
	( 99.55, 55.64) --
	( 84.71, 54.50) --
	( 69.87, 56.76) --
	( 55.03, 52.79) --
	cycle;

\path[] ( 55.03, 58.00) --
	( 69.87, 61.60) --
	( 84.71, 59.31) --
	( 99.55, 59.71) --
	(114.40, 58.63) --
	(129.24, 59.16) --
	(144.08, 61.71) --
	(158.92, 72.45) --
	(173.77, 81.74) --
	(188.61, 90.10) --
	(203.45, 98.38) --
	(218.29,109.54);

\path[] (218.29,109.46) --
	(203.45, 98.22) --
	(188.61, 86.26) --
	(173.77, 76.01) --
	(158.92, 66.75) --
	(144.08, 59.17) --
	(129.24, 54.26) --
	(114.40, 53.86) --
	( 99.55, 55.64) --
	( 84.71, 54.50) --
	( 69.87, 56.76) --
	( 55.03, 52.79);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 53.52) --
	( 69.87, 58.87) --
	( 84.71, 55.00) --
	( 99.55, 55.96) --
	(114.40, 54.84) --
	(129.24, 55.43) --
	(144.08, 59.55) --
	(158.92, 66.97) --
	(173.77, 76.82) --
	(188.61, 86.54) --
	(203.45, 98.25) --
	(218.29,109.50);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.24, 60.39) --
	(144.08, 68.57) --
	(158.92, 76.76) --
	(173.77, 84.94) --
	(188.61, 93.13) --
	(203.45,101.31) --
	(218.29,109.50);

\path[draw=drawColor,line width= 1.1pt,line join=round] (158.92, 60.39) --
	(173.77, 72.67) --
	(188.61, 84.94) --
	(203.45, 97.22) --
	(218.29,109.50);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (226.46,114.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.01, 57.54) --
	(129.24, 60.39) --
	(137.47, 57.54) --
	(137.47, 48.68) --
	(121.01, 48.68) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.70, 57.54) --
	(158.92, 60.39) --
	(167.15, 57.54) --
	(167.15, 48.68) --
	(150.70, 48.68) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (129.24, 49.23) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (158.92, 49.23) {$N^3$};
\end{scope}
\begin{scope}
\path[clip] (231.96,120.44) rectangle (411.55,194.74);
\definecolor{fillColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12,139.98) --
	(253.73,120.44) --
	(267.33,120.44) --
	(280.94,120.44) --
	(294.54,120.44) --
	(308.15,130.54) --
	(321.75,133.09) --
	(335.36,135.80) --
	(348.96,138.60) --
	(362.57,141.45) --
	(376.17,144.32) --
	(389.78,147.21) --
	(403.39,150.09);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 44.40) --
	(411.55, 44.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 71.59) --
	(411.55, 71.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 98.78) --
	(411.55, 98.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 58.00) --
	(411.55, 58.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 85.19) --
	(411.55, 85.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,112.38) --
	(411.55,112.38);

@@

\path[fill=fillColor,fill opacity=0.50] (240.12, 60.30) --
	(253.73, 64.90) --
	(267.33, 65.15) --
	(280.94, 69.28) --
	(294.54, 73.86) --
	(308.15, 75.13) --
	(321.75, 78.18) --
	(335.36, 83.17) --
	(348.96, 88.17) --
	(362.57, 93.25) --
	(376.17,101.77) --
	(389.78,104.80) --
	(403.39,111.56) --
	(403.39,111.28) --
	(389.78,104.61) --
	(376.17, 98.60) --
	(362.57, 93.17) --
	(348.96, 88.03) --
	(335.36, 83.04) --
	(321.75, 78.08) --
	(308.15, 73.15) --
	(294.54, 71.03) --
	(280.94, 68.63) --
	(267.33, 63.57) --
	(253.73, 60.00) --
	(240.12, 54.65) --
	cycle;

\path[] (240.12, 60.30) --
	(253.73, 64.90) --
	(267.33, 65.15) --
	(280.94, 69.28) --
	(294.54, 73.86) --
	(308.15, 75.13) --
	(321.75, 78.18) --
	(335.36, 83.17) --
	(348.96, 88.17) --
	(362.57, 93.25) --
	(376.17,101.77) --
	(389.78,104.80) --
	(403.39,111.56);

\path[] (403.39,111.28) --
	(389.78,104.61) --
	(376.17, 98.60) --
	(362.57, 93.17) --
	(348.96, 88.03) --
	(335.36, 83.04) --
	(321.75, 78.08) --
	(308.15, 73.15) --
	(294.54, 71.03) --
	(280.94, 68.63) --
	(267.33, 63.57) --
	(253.73, 60.00) --
	(240.12, 54.65);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12, 54.98) --
	(253.73, 60.57) --
	(267.33, 63.67) --
	(280.94, 68.67) --
	(294.54, 72.61) --
	(308.15, 73.27) --
	(321.75, 78.12) --
	(335.36, 83.10) --
	(348.96, 88.07) --
	(362.57, 93.19) --
	(376.17, 98.98) --
	(389.78,104.62) --
	(403.39,111.42);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (267.33, 63.09) --
	(280.94, 68.50) --
	(294.54, 73.67) --
	(308.15, 78.68) --
	(321.75, 83.56) --
	(335.36, 88.35) --
	(348.96, 93.06) --
	(362.57, 97.72) --
	(376.17,102.32) --
	(389.78,106.89) --
	(403.39,111.42);

\path[draw=drawColor,line width= 1.1pt,line join=round] (294.54, 62.31) --
	(308.15, 68.44) --
	(321.75, 74.58) --
	(335.36, 80.72) --
	(348.96, 86.86) --
	(362.57, 93.00) --
	(376.17, 99.14) --
	(389.78,105.28) --
	(403.39,111.42);

\path[draw=drawColor,line width= 1.1pt,line join=round] (321.75, 62.31) --
	(335.36, 70.49) --
	(348.96, 78.68) --
	(362.57, 86.86) --
	(376.17, 95.05) --
	(389.78,103.23) --
	(403.39,111.42);
\end{scope}
\begin{scope}
\path[clip] (231.96, 40.64) rectangle (411.55,114.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (247.22, 59.46) --
	(267.33, 63.09) --
	(284.57, 59.46) --
	(284.57, 48.65) --
	(247.22, 48.65) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (284.57, 59.46) --
	(294.54, 62.31) --
	(307.39, 59.46) --
	(307.39, 48.65) --
	(284.57, 48.65) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (313.52, 59.46) --
	(321.75, 62.31) --
	(329.98, 59.46) --
	(329.98, 50.60) --
	(313.52, 50.60) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (265.90, 51.15) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (295.98, 51.15) {$N^{1.5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (321.75, 51.15) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86,194.74) rectangle (226.46,211.31);
\definecolor{fillColor}{gray}{0.85}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 54.97) {1e-03};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 82.16) {1e-01};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91,109.35) {1e+01};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 58.00) --
	( 46.86, 58.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 85.19) --
	( 46.86, 85.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11,112.38) --
	( 46.86,112.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-05-07 07:42:34
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,120.44) --
	( 69.87,134.54) --
	( 84.71,140.87) --
	( 99.55,145.53) --
	(114.40,152.07) --
	(129.24,157.56) --
	(144.08,162.96) --
	(158.92,168.49) --
	(173.77,174.13) --
	(188.61,179.84) --
	(203.45,185.59) --
	(218.29,191.36);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 48.79) --
	(226.46, 48.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 74.31) --
	(226.46, 74.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 99.82) --
	(226.46, 99.82);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 61.55) --
	(226.46, 61.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 87.07) --
	(226.46, 87.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,112.58) --
	(226.46,112.58);

@@

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 56.99) --
	( 69.87, 57.03) --
	( 84.71, 57.32) --
	( 99.55, 60.60) --
	(114.40, 59.12) --
	(129.24, 60.73) --
	(144.08, 64.48) --
	(158.92, 69.92) --
	(173.77, 78.10) --
	(188.61, 89.04) --
	(203.45, 99.45) --
	(218.29,110.08) --
	(218.29,109.75) --
	(203.45, 98.66) --
	(188.61, 87.82) --
	(173.77, 77.86) --
	(158.92, 69.30) --
	(144.08, 62.34) --
	(129.24, 57.82) --
	(114.40, 55.88) --
	( 99.55, 58.18) --
	( 84.71, 53.31) --
	( 69.87, 52.48) --
	( 55.03, 52.46) --
	cycle;

\path[] ( 55.03, 56.99) --
	( 69.87, 57.03) --
	( 84.71, 57.32) --
	( 99.55, 60.60) --
	(114.40, 59.12) --
	(129.24, 60.73) --
	(144.08, 64.48) --
	(158.92, 69.92) --
	(173.77, 78.10) --
	(188.61, 89.04) --
	(203.45, 99.45) --
	(218.29,110.08);

\path[] (218.29,109.75) --
	(203.45, 98.66) --
	(188.61, 87.82) --
	(173.77, 77.86) --
	(158.92, 69.30) --
	(144.08, 62.34) --
	(129.24, 57.82) --
	(114.40, 55.88) --
	( 99.55, 58.18) --
	( 84.71, 53.31) --
	( 69.87, 52.48) --
	( 55.03, 52.46);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 53.27) --
	( 69.87, 52.94) --
	( 84.71, 53.71) --
	( 99.55, 59.11) --
	(114.40, 56.54) --
	(129.24, 58.38) --
	(144.08, 62.55) --
	(158.92, 69.56) --
	(173.77, 77.91) --
	(188.61, 87.87) --
	(203.45, 98.84) --
	(218.29,109.81);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.24, 63.73) --
	(144.08, 71.41) --
	(158.92, 79.09) --
	(173.77, 86.77) --
	(188.61, 94.45) --
	(203.45,102.13) --
	(218.29,109.81);

\path[draw=drawColor,line width= 1.1pt,line join=round] (158.92, 63.73) --
	(173.77, 75.25) --
	(188.61, 86.77) --
	(203.45, 98.29) --
	(218.29,109.81);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (226.46,114.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.01, 60.88) --
	(129.24, 63.73) --
	(137.47, 60.88) --
	(137.47, 52.02) --
	(121.01, 52.02) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.70, 60.88) --
	(158.92, 63.73) --
	(167.15, 60.88) --
	(167.15, 52.02) --
	(150.70, 52.02) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (129.24, 52.57) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (158.92, 52.57) {$N^3$};
\end{scope}
\begin{scope}
\path[clip] (231.96,120.44) rectangle (411.55,194.74);
\definecolor{fillColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12,120.44) --
	(253.73,120.44) --
	(267.33,120.44) --
	(280.94,120.44) --
	(294.54,120.44) --
	(308.15,130.54) --
	(321.75,133.09) --
	(335.36,135.80) --
	(348.96,138.60) --
	(362.57,141.45) --
	(376.17,144.32) --
	(389.78,147.21) --
	(403.39,150.09);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 48.79) --
	(411.55, 48.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 74.31) --
	(411.55, 74.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 99.82) --
	(411.55, 99.82);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 61.55) --
	(411.55, 61.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 87.07) --
	(411.55, 87.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,112.58) --
	(411.55,112.58);

@@

\path[fill=fillColor,fill opacity=0.50] (240.12, 59.86) --
	(253.73, 60.11) --
	(267.33, 63.24) --
	(280.94, 67.07) --
	(294.54, 71.40) --
	(308.15, 76.33) --
	(321.75, 81.19) --
	(335.36, 85.66) --
	(348.96, 90.13) --
	(362.57, 97.75) --
	(376.17,100.03) --
	(389.78,105.46) --
	(403.39,111.56) --
	(403.39,111.44) --
	(389.78,105.19) --
	(376.17, 99.67) --
	(362.57, 94.81) --
	(348.96, 89.66) --
	(335.36, 84.90) --
	(321.75, 80.54) --
	(308.15, 75.94) --
	(294.54, 71.18) --
	(280.94, 66.41) --
	(267.33, 61.49) --
	(253.73, 57.03) --
	(240.12, 53.14) --
	cycle;

\path[] (240.12, 59.86) --
	(253.73, 60.11) --
	(267.33, 63.24) --
	(280.94, 67.07) --
	(294.54, 71.40) --
	(308.15, 76.33) --
	(321.75, 81.19) --
	(335.36, 85.66) --
	(348.96, 90.13) --
	(362.57, 97.75) --
	(376.17,100.03) --
	(389.78,105.46) --
	(403.39,111.56);

\path[] (403.39,111.44) --
	(389.78,105.19) --
	(376.17, 99.67) --
	(362.57, 94.81) --
	(348.96, 89.66) --
	(335.36, 84.90) --
	(321.75, 80.54) --
	(308.15, 75.94) --
	(294.54, 71.18) --
	(280.94, 66.41) --
	(267.33, 61.49) --
	(253.73, 57.03) --
	(240.12, 53.14);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12, 53.54) --
	(253.73, 57.15) --
	(267.33, 61.65) --
	(280.94, 66.59) --
	(294.54, 71.33) --
	(308.15, 75.99) --
	(321.75, 80.60) --
	(335.36, 85.23) --
	(348.96, 89.69) --
	(362.57, 94.88) --
	(376.17, 99.75) --
	(389.78,105.24) --
	(403.39,111.49);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (253.73, 60.71) --
	(267.33, 66.14) --
	(280.94, 71.22) --
	(294.54, 76.07) --
	(308.15, 80.76) --
	(321.75, 85.34) --
	(335.36, 89.84) --
	(348.96, 94.26) --
	(362.57, 98.63) --
	(376.17,102.95) --
	(389.78,107.24) --
	(403.39,111.49);

\path[draw=drawColor,line width= 1.1pt,line join=round] (280.94, 63.10) --
	(294.54, 68.47) --
	(308.15, 73.85) --
	(321.75, 79.23) --
	(335.36, 84.60) --
	(348.96, 89.98) --
	(362.57, 95.36) --
	(376.17,100.73) --
	(389.78,106.11) --
	(403.39,111.49);

\path[draw=drawColor,line width= 1.1pt,line join=round] (321.75, 65.40) --
	(335.36, 73.08) --
	(348.96, 80.76) --
	(362.57, 88.44) --
	(376.17, 96.12) --
	(389.78,103.81) --
	(403.39,111.49);
\end{scope}
\begin{scope}
\path[clip] (231.96, 40.64) rectangle (411.55,114.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (233.62, 57.86) --
	(253.73, 60.71) --
	(270.96, 57.86) --
	(270.96, 47.05) --
	(233.62, 47.05) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (270.96, 57.86) --
	(280.94, 63.10) --
	(293.78, 57.86) --
	(293.78, 47.05) --
	(270.96, 47.05) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (313.52, 57.86) --
	(321.75, 65.40) --
	(329.98, 57.86) --
	(329.98, 49.00) --
	(313.52, 49.00) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (252.29, 49.55) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (282.37, 49.55) {$N^{1.4}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (321.75, 49.55) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86,194.74) rectangle (226.46,211.31);
\definecolor{fillColor}{gray}{0.85}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 58.52) {1e-03};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 84.04) {1e-01};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91,109.55) {1e+01};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 61.55) --
	( 46.86, 61.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 87.07) --
	( 46.86, 87.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11,112.58) --
	( 46.86,112.58);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
